Modeling the Graphotactics of Low-Resource Languages Using Sequential GANs

### 2022-05-11 Paper/paper.tex
reog continued

      TODO INCLUDE LINKS TO CODE ETC
  \bibliography{sources}
\end{document}

>>>>

    \section*{Code and Data}
    \subsection*{Written}
    \subsection*{Referenced}
    \begin{enumerate}
      \item Code from Anastasopoulos and Neubig, 2019: \url{https://github.com/antonisa/inflection}
      \item Stem alignment code from Mans Hulden: \url{https://github.com/mhulden/crpalign}
      \item GAN training routine from Géron: \url{https://github.com/ageron/handson-ml2/blob/master/17_autoencoders_and_gans.ipynb}
      \item Data for the SIGMORPHON 2019 shared task: \url{https://github.com/sigmorphon/2019}
      \item Wasserstein loss implementation: \url{https://machinelearningmastery.com/how-to-implement-wasserstein-loss-for-generative-adversarial-networks}
    \end{enumerate}
  \bibliography{sources}
\end{document}
